<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Benchmarks of functions from h6 package}
-->

  Benchmarking functions from **mypackage** package
=======================================

```{r, include=FALSE}
require(mypackage)
require(microbenchmark)
require(combinat)
```


Mode
------------

Let's construct a mode function in R and call it **mode2**:
```{r}
mode2 <- function(x) {
  m <- unique(x)
  m[which.max(tabulate(match(x, m)))]
}
```

Results on different input data:

```{r, cache=TRUE}
microbenchmark(mode(c(1:1000,1:999,1)), mode2(c(1:1000,1:999,1)))
microbenchmark(mode(c(1:1000,1:1000,1:1000,1)), mode2(c(1:1000,1:1000,1:1000,1)))
microbenchmark(mode(c(1:100000,100000:1,1)), mode2(c(1:100000,100000:1,1)))
```

**mode** from **mypackage** outperforms **mode2**.

simplify2array:
----------------------------
The goal was to build a function that whould mimic the behaviour of simplify2array from package base. The comparison will be done between **base::simplify2array** and **mypacage::simplify2array**
```{r, cache=TRUE}
microbenchmark(base::simplify2array(list(1:10000000,1:10000000)), mypackage::simplify2array(list(1:10000000,1:10000000)))

microbenchmark(base::simplify2array(list(1:10000,1:10000)), mypackage::simplify2array(list(1:10000,1:10000)))
```

**simplify2array** from **mypackage** outperforms **simplify2array** from **base**.

ass:
----------------------------
The goal was to build a function that whould mimic the behaviour of simplify2array from package base. The comparison will be done between **base::simplify2array** and **mypacage::simplify2array**

```{r}
ass2 <- function(x) {
  n = 2*x
  mat <- t(combn(n,x))
  matr <- matrix(0,nrow(mat),n)
  
  for (i in 1:nrow(matr)){
    matr[i,mat[i,]] <- 1
  }
  matr
}
```

```{r, cache=TRUE}
microbenchmark(ass(3), ass2(3))
microbenchmark(ass(8), ass2(8))
```

**ass** from **mypackage** outperforms **ass2**.
