<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{An Introduction to the mypackage}
-->
   
   An Introduction to **mypackage** package in R
=======================================

```{r, include=FALSE}
library(mypackage)
```


Introduction
------------
   
   
   The **mypackage** package is a solution for the homework 6 of Advanced Data Analysis Software Development with R course. Functions are written in **cpp**.



Functions:
----------------------------
   There are three functions included in the package:

- **mode** - returns the most frequent value from a given integer vector.
- **simplify2array** - mimics the behaviour of simplify2array from base package. The package will try to simplify the list of numeric vectors into a matrix. In case vectors in the list are of different size, function will generate an error.
- **ass** - generates all possible 0-1 assignment vectors of _2n_ survey participants in such a way that exactly _n_ of them are assigned to group 0 so call control group and the other _n_ ones are assigned to group 1 - treatment. The output is a matrix with all possible assignments.

Examples
-----------------------------

```{r}
mode(c(1,2,5,5,45,732,24,1,3,4,5,732,4,63))
simplify2array(list(1:4, 4:7))
ass(2)
```